\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-10-14 doc/flexiblesusy-paper.tex
address referee 1 comment 4a: diagonalization precision

\subsection{Tree-level spectrum}
\label{sec:TreeLevelSpectrum}
The tree-level \DRbar masses are calculated from the \DRbar\ model
parameters by diagonalizing the mass matrices returned from
\code{SARAH`MassMatrix[]}.  The numerical singular value decomposition
is performed by the Eigen library routine \code{Eigen::JacobiSVD} for
matrices with less than four rows and columns, and the LAPACK routines
\code{zgesvd}, \code{dgesvd} for larger matrices.  For the other types
of diagonalization, \code{Eigen::SelfAdjointEigenSolver} from Eigen is
used regardless of the matrix size.

>>>>

\subsection{Tree-level spectrum}
\label{sec:TreeLevelSpectrum}
The tree-level \DRbar masses are calculated from the \DRbar\ model
parameters by diagonalizing the mass matrices returned from
\code{SARAH`MassMatrix[]}.  The numerical singular value decomposition
is performed by the Eigen library routine \code{Eigen::JacobiSVD} for
matrices with less than four rows and columns, and the LAPACK routines
\code{zgesvd}, \code{dgesvd} for larger matrices.  For the other types
of diagonalization, \code{Eigen::SelfAdjointEigenSolver} from Eigen is
used regardless of the matrix size.  Note, that \fs uses double
precision floating point data types with $15$ significant digits to
store the mass matrices and the mass eigenvalues.  In case a particle
multiplet contains a very split mass hierarchy, where the mass
difference between the smallest and the largest mass in the multiplet
is of the order or greater than 10 orders of magnitude, double
precision data types are no longer sufficient.  In this case we
recommend to either split the multiplet into sub-multiplets with
smaller mass hierarchies, or integrate out the heavy states.
